Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-26 analysis/TAS_memo/memo_TAS_reviewers.Rmd
added table with defense bias

[INSERT TABLE]

>>>>

```{r inpts}
df <- data.frame( `Bias Pros` = c(1.5, 1.5, 1.5, 3.0, 3.0, 3.0, 1.5, 1.5, 1.5),
                  `Bias Def`= c(1.5, 1.5, 1.5, 3.0, 3.0, 3.0, 0.0, 0.0, 0.0),
                  `alpha`= c(0.1, 0.5, 1.0, 0.1, 0.5, 1.0, 0.1, 0.5, 1.0),
                  `Bias Det. Pros (95% CI)`= c(0.80, 0.99, 0.99, 0.99, 1.00, 1.00, 0.87, 1.00, 1.00))
knitr::kable(df, caption ="Simulation results showing effect of adjusting bias in defense on bias detection for the prosecutor. Changing the level of bias in defense does not alter bias detection rate for defense.", format = "latex", booktabs = TRUE, align = "c")
```
